---
title: 'CS Scripted: /l/-clarity Analysis'
author: "Page Piccinini"
date: "November 29, 2015"
output: html_document
---

```{r, echo=F, cache=F}
load("lclar_environment.RData")
```

# Model parameters

separate models for each language

dependent variable = F3 minus F2

fixed effects = context x word number x l position

random effects = 1) speaker as intercept and slope by context * word number * l position uncorrelated with intercept, 2) word as intercept and slope by context + word number uncorrelated with intercept, 3) sentence as intercept

# English: Overall results

```{r}
lclar_eng.lmer_sum
```

# English: Model comparisions

```{r}
lclar_eng_nocont.anova
lclar_eng_nown.anova
lclar_eng_nolpos.anova
lclar_eng_nocontxwn.anova
lclar_eng_nocontxlpos.anova
lclar_eng_nownxlpos.anova
lclar_eng_nocontxwnxlpos.anova
```

# Spanish: Overall results

```{r}
lclar_sp.lmer_sum
```

# Spanish: Model comparisions

```{r}
lclar_sp_nocont.anova
lclar_sp_nown.anova
lclar_sp_nolpos.anova
lclar_sp_nocontxwn.anova
lclar_sp_nocontxlpos.anova
lclar_sp_nownxlpos.anova
lclar_sp_nocontxwnxlpos.anova
```






